---
title: "Preliminary Sorting of Data"
output: html_notebook
---

Download all the libraries required
```{r}
library(quantmod)  #for downloading data/daily prices from various websites.
library(crypto) #fdownloading cryptocurrency prices from coinmarketcap.com
library(reshape2) 
library(xts)
library(magrittr) 
library(readxl) #make sure the package officer is detached before you run this chunk of code
library(xts)
library(PerformanceAnalytics)
library(rlist)
library(tidyverse)
library(ggthemes)

```
Aset universe:

1) Market Index              -- SP500 
2) Other Market Indicies     -- DJIA, NASDAQ
3) Sector Indices            -- Consumer Discretionary,	 Consumer Staple,	 Health Care,	 
                                Industrials ,	 Information Technology,	 Materials ,
                                Real Estate, Utilities, Communication Services,
                                Financials, Energy
4) Fixed Income Securities   -- 
5) Commodities               -- Gold, Silver, Crude Oil 
6) International Indices     -- NIKKEI, CAC 40, FTSE, Hang Seng Index, S&P BSE Sensex,
                                KOSPI, MOEX Index
7) Cryptocurrencies          -- BTC,LTC, XRP,XMR, XLM,ETH, EOS, BCH
8) Volatility Index          -- VIX
9) Risk Free Rate            -- 1-Month Treasury Constant Maturity Rate


1,2,3,4,5,6,8 --- Bloomberg
7         --- coinmarketcap.com
9         --- FRED

Extracting Cryptocurrency prices
```{r}


CryptoPrices <- crypto_history(coin = c("BCH","ETH", "XRP","BTC",
                                        "LTC","XMR","XLM","EOS"),
                                        start_date = '20190803')
CryptoPrices <- CryptoPrices[,c("symbol","date","close")]
CryptoPrices <- dcast(CryptoPrices,date ~ symbol, value.var = "close")
names(CryptoPrices)[1] <- "Dates"
CryptoPrices <- as.xts(CryptoPrices[,-1],order.by = CryptoPrices[,1])
CryptoPrices <- CryptoPrices[,c("BTC","LTC","XRP","XMR","ETH","EOS","BCH")]
#CryptoReturns <- diff(log(CryptoPrices)) 
```

Extracting from 1 month US Treasury rate from FRED using QuantMod library
```{r}

getSymbols('DGS1MO', src = 'FRED', from = as.Date("2013-04-23"), periodicity = "daily")

DGS1MO <- DGS1MO["2013-04-23/2020-04-30",]
```

Importing Prices for all the assets and storing it as an xts object.
```{r}
NoofAssets <- 57 # number of asset -- variables, columns in the file
#prices <- as.data.frame(read_xlsx("C:\\Users\\jrad2017\\OneDrive - Claremont Graduate University\\jmp\\new analysis\\Active Portfolio Management with Cryptocurrency\\portfolio assets.xlsx", sheet = "Rfile", col_types = c( "date", rep("numeric",NoofAssets)),na = c("NA", "#N/A" )))

prices <- as.data.frame(read_xlsx("/Users/jayantrao/OneDrive - Claremont Graduate University/jmp/new analysis/Active Portfolio Management with Cryptocurrency/portfolio assets.xlsx", sheet = "Rfile", col_types = c( "date", rep("numeric",NoofAssets)),na = c("NA", "#N/A" )))

prices <- as.xts(prices[,-1], order.by = prices[,1])
rm(NoofAssets)
```

Index of Assets and their Variable Names:
```{r}

#Index <- as.data.frame(read_xlsx("C:\\Users\\jrad2017\\OneDrive - Claremont Graduate University\\jmp\\new analysis\\Active Portfolio Management with Cryptocurrency\\portfolio assets.xlsx", sheet = "Rindex"))

Index <- as.data.frame(read_xlsx("/Users/jayantrao/OneDrive - Claremont Graduate University/jmp/new analysis/Active Portfolio Management with Cryptocurrency/portfolio assets.xlsx", sheet = "Rindex"))


#ClusteredIndex <- as.data.frame(read_xlsx("C:\\Users\\jrad2017\\OneDrive - Claremont Graduate University\\jmp\\new analysis\\Active Portfolio Management with Cryptocurrency\\portfolio assets.xlsx", sheet = "Clustered"))


ClusteredIndex <- as.list(read_xlsx("/Users/jayantrao/OneDrive - Claremont Graduate University/jmp/new analysis/Active Portfolio Management with Cryptocurrency/portfolio assets.xlsx", sheet = "Clustered"))


ClusteredIndex <- lapply(ClusteredIndex, function(x) x[!is.na(x)])
```

Creating Portfolios based on your asset or cluster choice(except cryptocurrencies) and selecting common dates 
If Cluster Use this
```{r}
Assets <- c("Market","Commodities","Fixed") #type in the Cluster symbol
ClusterAssets <- vector()
for(i in 1:length(Assets)){ClusterAssets <- append(ClusterAssets,ClusteredIndex[[Assets[i]]])}
ClusterAssets <- ClusterAssets %>% na.omit()
BasePort <- xts()
BasePort <- as.xts(x = prices[,c(ClusterAssets)], order.by = prices[,1])
rm(Assets,ClusterAssets, i)



```
If Individual Assets use this
```{r}
Assets <- c("SP500","DJIA","NASDAQ") #type in the asset symbol -- Refer Index
BasePort <-  BasePort %>% as.xts(x = prices[,c(Assets)], order.by = prices[,1])
rm(Assets)
```
Select only those dates which have values for all the selected assets and calculate their Ln returns.

```{r}

BasePort <- BasePort %>% na.omit() %>% Return.calculate(method = "log") %>% merge.xts(as.xts(x=prices[,"US1M"], order.by = prices[,1])/100, join= "inner") %>% na.omit()

colnames(BasePort)[ncol(BasePort)] <- "US1M"
```

Choice of Cryptocurrencies you want to add in your alternative portfolio
If you want all follow this:
```{r}
CryptoAssets <- prices[,ClusteredIndex[["Crypto"]]]
```
If you want to choose follow this: Make sure your list is given highest to lowest  datapoitns.
```{r}
Crypto <- c("BTC","LTC","XRP","ETH")
CryptoAssets <- as.xts(x = prices[,Crypto], order.by = prices[,1])
rm(Crypto)
```
Select only those dates which have values for all the selected assets and calculate their Ln returns.
```{r}

CryptoAssets <- Return.calculate(CryptoAssets, method = "log")
```

Creating a Full Portfolio :  Base + Crypto 
   AND
Subtracting RiskFreeRate from the assets to get excess returns -- US1M, after deannualizing it to daily interest rate (treated as risk free return)

```{r}
#creating a new function
'%!in%' <- function(x,y)!('%in%'(x,y))

FullPortBackTesting <- FullPort <- merge.xts(BasePort,CryptoAssets,join = "inner")

FullPortBackTesting <- subset(FullPortBackTesting, select = -c(get("US1M")))

days <- 252 # 252 check 
B <- coredata(FullPort)
date <- index(FullPort)
B <- B - (((1+B[,"US1M"])^(1/days))-1)
B <- subset(B,select = -c(get("US1M")))
FullPort <- as.xts(B,order.by = date)
rm(date, B, days)

AssetNames <- list(BaseNames = names(FullPort)[names(FullPort)%!in% 
                                                 names(CryptoAssets)], AltNames = names(FullPort))
rm(BasePort,CryptoAssets)
```

Creating Sub-Portfolios for Base and Alternative: Base + Crypto 
Procedure : Fixed Window : 500 obs , Rebalance = Every 30 days
1) Every subportfolio has 500 observations for each Asset 
2) Rebalancing happens every 30 days. (This is arbitrary)

```{r}

Fixedwindow <- 500 #days
Rebalance <- 30 #days

SubFull <- list()   
Port <- FullPort 


for(i in seq(from = Fixedwindow, to = nrow(Port), by = Rebalance)){
  
  startindex <- i - Fixedwindow + 1
  endindex   <- i
  
  assets <- Port[startindex:endindex,]
  
  for (j in 1:ncol(assets)){
    
    if(sum(is.na(assets[,j])) < 1) {#check column wise if is.na(column) > nuber of observations or % of the windowsize, drop the variable
      if(j == 1){AssetsFinallyConsidered <- assets[,j]}
      else{AssetsFinallyConsidered = merge.xts(AssetsFinallyConsidered,assets[,j])}
    }
  }
  print("Total NAs in the Sub-portfolio:",sum(is.na(AssetsFinallyConsidered[,])))
  SubFull <- list.append(SubFull, AssetsFinallyConsidered) 
}


Dates <- data.frame(matrix(nrow = Fixedwindow, ncol = length(SubFull)))
for(PeriodNo in 1:list.count(SubFull)){Dates[,PeriodNo] <- index(SubFull[[PeriodNo]])}

rm(i,j, startindex, endindex, assets, Fixedwindow, Rebalance, Port, AssetsFinallyConsidered, PeriodNo)
```
Creating Sub Portfolios for Backtesting (refer 5, 5b Backtesting)
```{r}

Fixedwindow <- 500 #days
Rebalance <- 30 #days

SubFullBackTesting <-  list()   
Port <- FullPortBackTesting


for(i in seq(from = Fixedwindow, to = nrow(Port), by = Rebalance)){
  
  startindex <- i - Fixedwindow + 1
  endindex   <- i
  
  assets <- Port[startindex:endindex,]
  
  for (j in 1:ncol(assets)){
    
    if(sum(is.na(assets[,j])) < 1) {#check column wise if is.na(column) > nuber of observations or % of the windowsize, drop the variable
      if(j == 1){AssetsFinallyConsidered <- assets[,j]}
      else{AssetsFinallyConsidered = merge.xts(AssetsFinallyConsidered,assets[,j])}
    }
  }
  print("Total NAs in the Sub-portfolio:",sum(is.na(AssetsFinallyConsidered[,])))
  SubFullBackTesting <- list.append(SubFullBackTesting, AssetsFinallyConsidered) 
  
}


DatesBack <- data.frame(matrix(nrow = Fixedwindow, ncol = length(SubFull)))
for(PeriodNo in 1:list.count(SubFull)){

DatesBack[,PeriodNo] <- index(SubFull[[PeriodNo]])
}

rm(i,j, startindex, endindex, assets, Fixedwindow, Rebalance, Port, AssetsFinallyConsidered)
```

Creating a function that converts an unequal list of lists to a dataframe -- very useful going forward.
```{r}
Unequal_df <- function(LIST){
  
  NoofRebalPeriod <- length(LIST)

  out <-   data.frame(matrix(nrow = NoofRebalPeriod, ncol = length(LIST[[NoofRebalPeriod]])))
  colnames(out)  <- names(LIST[[NoofRebalPeriod]])  

  for (PeriodNo in 1:NoofRebalPeriod){
    unlis <-  unlist(LIST[[PeriodNo]])
    out[PeriodNo,names(unlis)] <- t(unlis) 
    rm(unlis)  
    }
output <- out  
}

```
SANITY CHECK : Calculate the subportfolio means for each asset in the subportfolio
```{r}

SubFull_Mean <- lapply(SubFull,colMeans)
SubFull_Mean <- Unequal_df(SubFull_Mean)
```
You may remove the Mean Dataframe once you are done checking the numbers
```{r}
rm(SubFull_Mean)
```


PROCESS 2: Univariate Modelling for each of the assets in the subportfolio using univariate Modelling.Rmd


EXTRASSSSSSSS:

Creating Scatter Plots for every pair of asset.

```{r}
data <- prices  %>%  select(c("Dates","ETH","SILVER")) %>% na.omit()
data <-   as.xts(data[,-1], order.by = data[,1]) %>% Return.calculate(method = "log") %>% as.data.frame() %>% rownames_to_column(var= "Dates") 

data <-  data %>% mutate(Year = format(as.Date(Dates),'%Y'),Month = format(as.Date(Dates),'%m') , Day = format(as.Date(Dates),'%d'))


ggplot(data,aes_string(x = colnames(data)[2], y =colnames(data)[3])) + 
                                             geom_point(color = "Magenta", shape = 1)+ facet_wrap(~Year) + theme_economist_white()+
                                             theme(plot.title = element_text(margin = margin(t = 50, b = -5), hjust = 0.5),
                                                   axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
                                                   axis.title.x = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))




```













