---
title: "Univariate Modelling"
output: html_notebook
---

```{r}
library(rugarch)
library(lestat)
library(gdata)
library(stats)
library(fBasics)
library(tictoc)
```

SUB-PORTFOLIOS   -----------  UNIVARIATE MARGINAL DISTRIBUTION MODELLING

1) ARMA-GARCH Modelling

Select one of the models from below

i)
gjr.arma0.0 <- ugarchspec(variance.model = list(model = "gjrGARCH", garchOrder = c(1,1), submodel = NULL, external.regressors = NULL, variance.targeting = FALSE),
                  mean.model = list(armaOrder = c(0, 0)), distribution.model = "sstd", start.pars = list(),fixed.pars = list())

ii)
gjr.arma1.0 <- ugarchspec(variance.model = list(model = "gjrGARCH", garchOrder = c(1,1), submodel = NULL, external.regressors = NULL, variance.targeting = FALSE),
                          mean.model = list(armaOrder = c(1, 0)), distribution.model = "sstd", start.pars = list(),fixed.pars = list())

iii)
gjr.arma1.1 <- ugarchspec(variance.model = list(model = "gjrGARCH", garchOrder = c(1,1), submodel = NULL, external.regressors = NULL, variance.targeting = FALSE),
                          mean.model = list(armaOrder = c(1, 1)), distribution.model = "sstd", start.pars = list(),fixed.pars = list())

iv)
garch.arma0.0 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1,1), variance.targeting = TRUE),
                             mean.model = list(armaOrder = c(0, 0)), distribution.model = "sstd")
garch.arma1.0 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1,1), submodel = NULL, external.regressors = NULL, variance.targeting = FALSE),
                            mean.model = list(armaOrder = c(1, 0)), distribution.model = "sstd", start.pars = list(),fixed.pars = list())

v)
garch.arma1.1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1,1), submodel = NULL, external.regressors = NULL, variance.targeting = FALSE),
                            mean.model = list(armaOrder = c(1, 1)), distribution.model = "sstd", start.pars = list(),fixed.pars = list())

```{r}

Model <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1,1)
                                          ,submodel = NULL, external.regressors = NULL,
                                          variance.targeting = FALSE),
                    mean.model = list(armaOrder = c(0, 0)),
                    distribution.model = "sstd", start.pars = list(),fixed.pars = list())
```


```{r}
AssetReturns <- SubFull
NoofRebalPeriod <-length(AssetReturns)


Modelfit <- CondHTEMP  <- ConvergenceTEMP <- GARCHModelTEMP <- DistributionTEMP <-rep(list(list()),NoofRebalPeriod)
CondH <- Convergence <-  GARCHModel <- Distribution <- data.frame(matrix(nrow = NoofRebalPeriod, ncol = ncol(AssetReturns[[NoofRebalPeriod]])))
colnames(CondH) <- colnames(Convergence) <- colnames(GARCHModel) <- colnames(Distribution) <- names(AssetReturns[[NoofRebalPeriod]])


for ( PeriodNo in 1:NoofRebalPeriod){
  NoofAssets <- ncol(AssetReturns[[PeriodNo]])
  Modelfit[[PeriodNo]] <- rep(list(list()),NoofAssets)
  CondHTEMP[[PeriodNo]] <- ConvergenceTEMP[[PeriodNo]] <- GARCHModelTEMP[[PeriodNo]] <-      
    DistributionTEMP[[PeriodNo]] <-  vector(mode = "logical", length = NoofAssets)
  names(CondHTEMP[[PeriodNo]]) <- names(ConvergenceTEMP[[PeriodNo]]) <- names(GARCHModelTEMP[[PeriodNo]]) <- 
    names(DistributionTEMP[[PeriodNo]]) <- colnames(AssetReturns[[PeriodNo]])

  for (AssetNo in 1:NoofAssets){
    Modelfit[[PeriodNo]][[AssetNo]] <-  ugarchfit(data = AssetReturns[[PeriodNo]][,AssetNo],spec = Model, solver = 
                                                    "hybrid")
    CondHTEMP[[PeriodNo]][AssetNo]        <-   Modelfit[[PeriodNo]][[AssetNo]]@fit[["condH"]]
    ConvergenceTEMP[[PeriodNo]][AssetNo]  <-   Modelfit[[PeriodNo]][[AssetNo]]@fit[["convergence"]]
    GARCHModelTEMP[[PeriodNo]][AssetNo] <- Modelfit[[PeriodNo]][[AssetNo]]@model[["modeldesc"]][["vmodel"]]
    DistributionTEMP[[PeriodNo]][AssetNo] <- Modelfit[[PeriodNo]][[AssetNo]]@model[["modeldesc"]][["distribution"]]
  }
  names(Modelfit[[PeriodNo]]) <- names(AssetReturns[[PeriodNo]])  
    
  unlis <-  unlist(CondHTEMP[[PeriodNo]])
  CondH[PeriodNo,names(unlis)] <- t(unlis) 
  rm(unlis)
  unlis <-  unlist(ConvergenceTEMP[[PeriodNo]])
  Convergence[PeriodNo,names(unlis)] <- t(unlis) 
  rm(unlis)
  unlis <-  unlist(GARCHModelTEMP[[PeriodNo]])
  GARCHModel[PeriodNo,names(unlis)] <- t(unlis) 
  rm(unlis)
  unlis <-  unlist(DistributionTEMP[[PeriodNo]])
  Distribution[PeriodNo,names(unlis)] <- t(unlis) 
  rm(unlis)
}

ModelFit <- list(Modelfit = Modelfit, CondH = CondH, Convergence = Convergence, GARCHModel = GARCHModel, Distribution = Distribution)

rm(AssetReturns,NoofRebalPeriod,NoofAssets,PeriodNo,AssetNo,Model,ConvergenceTEMP, CondHTEMP,Modelfit,CondH,Convergence, DistributionTEMP,GARCHModelTEMP,Distribution,GARCHModel)

```

Extracting the Standardized Residuals

```{r}
#@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
Modelfit <- ModelFit[["Modelfit"]]
observations <-  500 
#@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
NoofRebalPeriod <- length(Modelfit)
StdzedResiduals <- rep(list(list()),NoofRebalPeriod)

for (PeriodNo in 1:NoofRebalPeriod){
  NoofAssets <- length(Modelfit[[PeriodNo]])
  StdzedResiduals[[PeriodNo]] <- matrix(nrow = observations , ncol = NoofAssets)
  colnames(StdzedResiduals[[PeriodNo]])   <-   names(Modelfit[[PeriodNo]])
  AssetnameS <- names(Modelfit[[PeriodNo]])
  for (AssetNo in 1 : NoofAssets){  
    AssetnamE <- AssetnameS[AssetNo]
    StdzedResiduals[[PeriodNo]][,AssetnamE] <- rugarch::residuals(Modelfit[[PeriodNo]][[AssetnamE]] 
                                                                  ,standardize =TRUE)
  }
}


#@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
Std.Resids <- StdzedResiduals
#@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

rm(Modelfit,NoofRebalPeriod,NoofAssets,PeriodNo,AssetNo,StdzedResiduals, observations, AssetnameS,AssetnamE)

```



EXTRACT the ARMA-GARCH Parameters
(The below codes are assuming the same number of parameters for all the Assets.)

```{r}

Modelfit <- ModelFit[["Modelfit"]]

NoofRebalPeriod <- length(Modelfit)
  
ParamList <- rep(list(list()),NoofRebalPeriod)

for(PeriodNo in 1:NoofRebalPeriod){
  NoofAssets <- length(Modelfit[[PeriodNo]])
  cnames <- names(Modelfit[[PeriodNo]])
  rnames <- names(Modelfit[[1]][[1]]@fit[["coef"]]) #using the first asset from period 1 for the coef names.
  ParamList[[PeriodNo]] <- rep(list(matrix(nrow = length(rnames) , ncol = NoofAssets, dimnames = list(rnames, 
                                                                                                      cnames))),3)
  names(ParamList[[PeriodNo]]) <- c("Parameters","RobustStdErrors","Tvalues")
  for (AssetNo in 1:NoofAssets){
    ParamList[[PeriodNo]][[1]][,AssetNo] <- round(Modelfit[[PeriodNo]][[AssetNo]]@fit[["coef"]],4)
    ParamList[[PeriodNo]][[2]][,AssetNo] <- round(Modelfit[[PeriodNo]][[AssetNo]]@fit[["robust.se.coef"]],4)
    ParamList[[PeriodNo]][[3]][,AssetNo] <- round(Modelfit[[PeriodNo]][[AssetNo]]@fit[["robust.tval"]],4)
  }
}
Parameters <- ParamList  

rm(Modelfit, PeriodNo,AssetNo,NoofAssets,NoofRebalPeriod,cnames,rnames,ParamList)


```

                                    Empirical and Parametric Distribution    
 
 Parametric Distribution of the STD Resids #######
 
 1) Fit the distribution i.e consider the parameters
```{r}

StdResTEMP <- Std.Resids
ParamTEMP <- Parameters
NoofRebalPeriod =length(StdResTEMP)
observations = 500
PITTemp <- rep(list(list()),NoofRebalPeriod)
for (PeriodNo in 1:NoofRebalPeriod){
    DistTemp <- ParamTEMP[[PeriodNo]][["Parameters"]][(nrow(ParamTEMP[[PeriodNo]][["Parameters"]])-1):
                                                        nrow(ParamTEMP[[PeriodNo]][["Parameters"]]),]
    NoofAssets <- ncol(DistTemp) 
    cnames <- colnames(StdResTEMP[[PeriodNo]])
    PITTemp[[PeriodNo]] <-  matrix(nrow = observations, ncol = NoofAssets, dimnames = list(NULL,cnames))
    for ( AssetNo in 1:NoofAssets){ 
       PITTemp[[PeriodNo]][,AssetNo] <- pdist(distribution = "sstd",StdResTEMP[[PeriodNo]][,AssetNo],
                                              mu= 0, sigma = 1, skew = DistTemp["skew",AssetNo], 
                                              shape = DistTemp["shape",AssetNo])
                                                
    }
}

PIT <- PITTemp

rm(observations,PeriodNo,AssetNo,NoofRebalPeriod,NoofAssets,DistTemp,ParamTEMP,StdResTEMP,PITTemp,cnames)
```


2)  empirical CDF
```{r}

ResTEMP <- Std.Resids
observations = 500
NoofRebalPeriod = length(ResTEMP)
EmpTEMP <- rep(list(list()),NoofRebalPeriod)
for (PeriodNo in 1:NoofRebalPeriod){
  NoofAssets = ncol(ResTEMP[[PeriodNo]]) 
  cnames <- colnames(ResTEMP[[PeriodNo]])
  EmpTEMP[[PeriodNo]] <-  matrix(nrow = observations, ncol = NoofAssets, dimnames = list(NULL,cnames))
  
  for (AssetNo in 1: NoofAssets){
    empiricalCDF <- ecdf(ResTEMP[[PeriodNo]][,AssetNo])
    EmpTEMP[[PeriodNo]][,AssetNo] <-  empiricalCDF(ResTEMP[[PeriodNo]][,AssetNo])
  }
}  

EMP <- EmpTEMP

rm(observations,cnames,PeriodNo,AssetNo,NoofRebalPeriod,NoofAssets,empiricalCDF, EmpTEMP, ResTEMP)
```

Join them together in UniformDist

```{r}
UniformDist <- list(Udist = PIT,  Uedf = EMP)

rm(PIT,EMP)
```

PROCESS 3: Joint Dependence Structure using Vine Copula -- refer to Copula codes.Rmd
                       
                       





