---
title: "Portfolio Optimization"
output: html_notebook
---

Producing some preliminary results to see how the simulated results look

```{r, echo=FALSE, include=FALSE}
library(fBasics)
library(readxl)
library(gdata)
library(PortfolioAnalytics)
library(PerformanceAnalytics)
library(ROI)
library(flextable)
library(officer)
library(dplyr)
library(gdata)
library(profvis)
library(tictoc)
library(rlist)
library(parallel)
library(DEoptim)
library(pso)
library(GenSA)
library(pbmcapply)
```

```{r}
Unequal_df <- function(LIST){
  
NoofRebalPeriod <- length(LIST)

out <-   data.frame(matrix(nrow = NoofRebalPeriod, ncol = length(LIST[[NoofRebalPeriod]])))
colnames(out)  <- names(LIST[[NoofRebalPeriod]])  

for (PeriodNo in 1:NoofRebalPeriod){
unlis <-  unlist(LIST[[PeriodNo]])
  out[PeriodNo,names(unlis)] <- t(unlis) 
  rm(unlis)  
}
output <- out  
}
```


With the set of simulated returns I will be optimizing the portoflio (calculating the optimal portfolio weights) using different optimization techniques.

Optimization Techniques

1) 1/N or Naive Portfolio
2) Minimum Standard Deviation Portfolio
3) Minimum Expected Shortfall Portfolio
4) Sharpe Portfolio
5) STARR Portfolio
6) Maximum Mean Portfolio

Initializing the variables -- PortfolioWeights and PortfolioOptimization.
```{r, echo=FALSE}

PortfolioWeights <- list(Base = list(NaivePortfolio = list(), MinSD = list(), MinES = list(), Sharpe = list(), Starr = list(), MaxMean = list()), Alt = list(NaivePortfolio = list(), MinSD = list(), MinES = list(), Sharpe = list(), Starr = list(), MaxMean = list()))

PortfolioOptimization <- list(Base = list(MinSD = list(), MinES = list(), Sharpe = list(), Starr = list(), MaxMean = list()), Alt = list(MinSD = list(), MinES = list(), Sharpe = list(), Starr = list(), MaxMean = list()))
```

1) 1/N or Naive Portfolio

```{r, echo=FALSE}

for(PortType in 1:2){

if (length(PortfolioWeights[[PortType]][["NaivePortfolio"]]) != 0 ){PortfolioWeights[[PortType]][["NaivePortfolio"]] <- list()}

simreturns <- Sim.Returns[[PortType]]
Pweights <- list()

for (CopulaType in 1:4){
  AssetsforOptimization = simreturns[[CopulaType]]
  NoofRebalPeriod = length(AssetsforOptimization)

  weights <- list()

  for (PeriodNo in 1:NoofRebalPeriod){
    NoofAssets <- ncol(AssetsforOptimization[[PeriodNo]])
    
    Rownames <- colnames(AssetsforOptimization[[PeriodNo]])
    TempWeights <- as.numeric(rep(1/NoofAssets, each = NoofAssets))
    names(TempWeights) <- Rownames
    weights <- list.append(weights,TempWeights)
  }
  weights <- Unequal_df(weights)
  Pweights <- list.append(Pweights, weights)
}

  names(Pweights) <- c("P.R.Naive.Weights","P.C.Naive.Weights","E.R.Naive.Weights","E.C.Naive.Weights")
  PortfolioWeights[[PortType]][["NaivePortfolio"]] <- Pweights

  rm(AssetsforOptimization, PeriodNo, NoofAssets, Rownames,TempWeights, weights, CopulaType, NoofRebalPeriod, 
     simreturns)
}
rm(PortType)
```

2) Minimum Standard Deviation Portfolio

```{r,echo=FALSE}
for(PortType in 1:2){
  tic(sprintf("PortType %d", PortType))     
  if (length(PortfolioWeights[[PortType]][["MinSD"]]) != 0 )
    {PortfolioWeights[[PortType]][["MinSD"]] <- list()}
  if (length(PortfolioOptimization[[PortType]][["MinSD"]]) != 0 )
    {PortfolioOptimization[[PortType]][["MinSD"]] <- list()}
    
  simreturns <- Sim.Returns[[PortType]]
  Pweights <- list()
  Popt <- list()
  
  for (CopulaType in 1:4){
    tic(sprintf("CopulaType %d", CopulaType))    
    AssetsforOptimization = simreturns[[CopulaType]]
    NoofRebalPeriod = length(AssetsforOptimization)
    weights <-  opt <- list()
    
    MinSDOpt <- function(AssetOptim){
                      init.portfolio <- portfolio.spec(assets = colnames(AssetOptim))
                      #init.portfolio <- add.constraint(portfolio = init.portfolio, type = "full_investment") or
                       init.portfolio <- add.constraint(portfolio = init.portfolio, type = "weight_sum", 
                                                       min_sum = 0.99, max_sum = 1.01) 
                       init.portfolio <- add.constraint(portfolio = init.portfolio, type = "long_only") 
                     
                      init.portfolio <- add.objective(portfolio=init.portfolio, type="risk", name="var")
                      optimized <- optimize.portfolio(R = AssetOptim, portfolio = init.portfolio, 
                                         optimize_method = "ROI",trace = TRUE,message = T)
                      out <- optimized
                      return(out)
    }
    
    numCores <- detectCores() 
    opt <- pbmcapply::pbmclapply(AssetsforOptimization,MinSDOpt, mc.cores = numCores)
    weights <- lapply(opt, function(x){x$weights})
    
    weights <- Unequal_df(weights)
    Pweights <- list.append(Pweights, weights)
    
    Popt <- list.append(Popt, opt)
    toc()
  }
  names(Pweights) <- c("P.R.MinSD.Weights","P.C.MinSD.Weights","E.R.MinSD.Weights","E.C.MinSD.Weights")
  
  names(Popt) <- c("P.R.MinSD.Optimization","P.C.MinSD.Optimization","E.R.MinSD.Optimization","E.C.MinSD.Optimization")
  PortfolioWeights[[PortType]][["MinSD"]] <- Pweights
  PortfolioOptimization[[PortType]][["MinSD"]] <- Popt
  rm(opt,weights, CopulaType, NoofRebalPeriod, AssetsforOptimization,simreturns)
  toc()
}

rm(PortType)

```

3) Minimum Expected Shortfall Portfolio

```{r}
for(PortType in 2){
  tic(sprintf("PortType %d", PortType))    
  if (length(PortfolioWeights[[PortType]][["MinES"]]) != 0 )
    {PortfolioWeights[[PortType]][["MinES"]] <- list()}
  if (length(PortfolioOptimization[[PortType]][["MinES"]]) != 0 )
    {PortfolioOptimization[[PortType]][["MinES"]] <- list()}
    
  simreturns <- Sim.Returns[[PortType]]
  Pweights <- list()
  Popt <- list()
  
  if (length(PortfolioWeights[["MinES"]]) != 0 )
    {PortfolioWeights[["MinES"]] <- list()}
  if (length(PortfolioOptimization[["MinES"]]) != 0 )
    {PortfolioOptimization[["MinES"]] <- list()}
  
  for (CopulaType in 1){
    tic(sprintf("CopulaType %d", CopulaType))    
    AssetsforOptimization = simreturns[[CopulaType]]
    NoofRebalPeriod = length(AssetsforOptimization)
    weights <- opt <- list()
    
      MinESopt <- function(AssetOptim){
                  init.portfolio <- portfolio.spec(assets = colnames(AssetOptim))
                 #init.portfolio <- add.constraint(portfolio = init.portfolio, type = "full_investment") or
                       init.portfolio <- add.constraint(portfolio = init.portfolio, type = "weight_sum", 
                                                       min_sum = 0.99, max_sum = 1.01) 
                       init.portfolio <- add.constraint(portfolio = init.portfolio, type = "long_only") 
                  
                  init.portfolio <- add.objective(portfolio=init.portfolio, type="risk", name="ES", arguments=list(method = c("historical")))
                  optimized <- optimize.portfolio(R = AssetOptim, portfolio = init.portfolio, 
                           optimize_method = "ROI",trace = TRUE,message = T)
                  out <- optimized
                  return(out)
                  }
    numCores <- detectCores() - 2
    opt <- pbmcapply::pbmclapply(AssetsforOptimization,MinESopt, mc.cores = numCores)
    weights <- lapply(opt, function(x){x$weights})
    weights <- Unequal_df(weights)
    Pweights <- list.append(Pweights, weights)
    Popt <- list.append(Popt, opt)
    toc()
  }
  names(Pweights) <- c("P.R.MinES.Weights","P.C.MinES.Weights","E.R.MinES.Weights","E.C.MinES.Weights")
  names(Popt) <- c("P.R.MinES.Optimization","P.C.MinES.Optimization","E.R.MinES.Optimization","E.C.MinES.Optimization")
  
  PortfolioWeights[[PortType]][["MinES"]] <- Pweights
  PortfolioOptimization[[PortType]][["MinES"]] <- Popt
  
  rm(opt, weights, CopulaType, NoofRebalPeriod, init.portfolio, AssetsforOptimization, simreturns)
  toc()
}
rm(PortType)
```

4) Sharpe Portfolio

```{r}
PortType <- 1
for (PortType in 1:2){
  tic(sprintf("PortType %d", PortType))    
  if(length(PortfolioWeights[[PortType]][["Sharpe"]]) != 0 ){
      PortfolioWeights[[PortType]][["Sharpe"]] <- list()
  }
  if(length(PortfolioOptimization[[PortType]][["Sharpe"]]) != 0 ){
    PortfolioOptimization[[PortType]][["Sharpe"]] <- list()
  }

  simreturns <- Sim.Returns[[PortType]]
  Pweights <- list()
  Popt <- list()
  #CopulaType <- 1
  for (CopulaType in 1:4){
    tic(sprintf("CopulaType %d", CopulaType))   
    AssetsforOptimization = simreturns[[CopulaType]]
    NoofRebalPeriod = length(AssetsforOptimization)
    weights <-  opt <- list()
  
     Sharpeopt <- function(AssetOptim){
                  init.portfolio <- portfolio.spec(assets = colnames(AssetOptim))
                  #init.portfolio <- add.constraint(portfolio = init.portfolio, type = "full_investment") or
                  init.portfolio <- add.constraint(portfolio = init.portfolio, type = "weight_sum", 
                                                       min_sum = 0.99, max_sum = 1.01) 
                  init.portfolio <- add.constraint(portfolio = init.portfolio, type = "long_only") 
                  
                  
                  init.portfolio <- add.objective(portfolio=init.portfolio,type="return", name="mean")
                  init.portfolio <- add.objective(portfolio=init.portfolio,type="risk", name="StdDev")
                  optimized <- optimize.portfolio(R = AssetOptim, portfolio = init.portfolio, 
                           optimize_method = "ROI",trace = TRUE, maxSR = TRUE,message = T)
                  out <- optimized[-2]
                  return(out)
                  }
    numCores <- detectCores() 
    opt <- pbmcapply::pbmclapply(AssetsforOptimization,Sharpeopt, mc.cores = numCores)
    weights <- lapply(opt, function(x){x$weights})
    weights <- Unequal_df(weights)
    Pweights <- list.append(Pweights, weights)
    Popt <- list.append(Popt, opt)
    toc()
}
names(Pweights) <- c("P.R.Sharpe.Weights","P.C.Sharpe.Weights","E.R.Sharpe.Weights","E.C.Sharpe.Weights")
names(Popt) <- c("P.R.Sharpe.Optimization","P.C.Sharpe.Optimization","E.R.Sharpe.Optimization","E.C.Sharpe.Optimization")


PortfolioWeights[[PortType]][["Sharpe"]] <- Pweights
PortfolioOptimization[[PortType]][["Sharpe"]] <- Popt

rm(opt, weights, CopulaType, NoofRebalPeriod, init.portfolio, AssetsforOptimization,simreturns)
toc()
}
rm(PortType)
```

5) STARR Portfolio

```{r}

for (PortType in 1:2){
  tic(sprintf("PortType %d", PortType))  
  if (length(PortfolioWeights[[PortType]][["Starr"]]) != 0 ){PortfolioWeights[[PortType]][["Starr"]] <- list()}
  if (length(PortfolioOptimization[[PortType]][["Starr"]]) != 0 ){PortfolioOptimization[[PortType]][["Starr"]] <- list()}

  simreturns <- Sim.Returns[[PortType]]
  Pweights <- list()
  Popt <- list()  
  
  for (CopulaType in 1:4){
    tic(sprintf("CopulaType %d", CopulaType))  
    AssetsforOptimization = simreturns[[CopulaType]]
    NoofRebalPeriod = length(AssetsforOptimization)
    weights <-  opt <- list()
    
    Staropt <- function(AssetOptim){
                        init.portfolio <- portfolio.spec(assets = colnames(AssetOptim))
                        #init.portfolio <- add.constraint(portfolio = init.portfolio, type = "full_investment") or
                        init.portfolio <- add.constraint(portfolio = init.portfolio, type = "weight_sum", 
                                                       min_sum = 0.99, max_sum = 1.01) 
                        init.portfolio <- add.constraint(portfolio = init.portfolio, type = "long_only") 
                        
                        
                        init.portfolio <- add.objective(portfolio=init.portfolio, type="risk", name="ES")
                        init.portfolio <- add.objective(portfolio=init.portfolio, type="return", name="mean")
                        optimized <- optimize.portfolio(R = AssetOptim, portfolio = init.portfolio, 
                                 optimize_method = "ROI",trace = TRUE, maxSR = TRUE,message = T)
                        out <- optimized
                        return(out)
                        }
    numCores <- detectCores() 
    opt <- pbmcapply::pbmclapply(AssetsforOptimization,Staropt, mc.cores = numCores)
    weights <- lapply(opt, function(x){x$weights})


    weights <- Unequal_df(weights)
    Pweights <- list.append(Pweights, weights)
    Popt <- list.append(Popt, opt)
    
    toc()
  }
  names(Pweights) <- c("P.R.Starr.Weights","P.C.Starr.Weights","E.R.Starr.Weights","E.C.Starr.Weights")
  names(Popt) <- c("P.R.Starr.Optimization","P.C.Starr.Optimization","E.R.Starr.Optimization","E.C.Starr.Optimization")
  
  PortfolioWeights[[PortType]][["Starr"]] <- Pweights
  PortfolioOptimization[[PortType]][["Starr"]] <- Popt
  
  
  rm(opt, weights, CopulaType, NoofRebalPeriod, AssetsforOptimization, simreturns)
  toc()
}

rm(PortType)
```

6) Maximum Mean Portfolio

```{r}

for (PortType in 1:2){

  if (length(PortfolioWeights[[PortType]][["MaxMean"]]) != 0 )
    {PortfolioWeights[[PortType]][["MaxMean"]] <- list()}
  if (length(PortfolioOptimization[[PortType]][["MaxMean"]]) != 0 )
    {PortfolioOptimization[[PortType]][["MaxMean"]] <- list()}
  
  simreturns <- Sim.Returns[[PortType]]
  Pweights <- list()
  Popt <- list()  
  
  for (CopulaType in 1:4){
    AssetsforOptimization = simreturns[[CopulaType]]
    NoofRebalPeriod = length(AssetsforOptimization)
    weights <-  opt <- list()
    
    
      MaxMeanopt <- function(AssetOptim){
                            init.portfolio <- portfolio.spec(assets = colnames(AssetOptim))
                            #init.portfolio <- add.constraint(portfolio = init.portfolio, type = "full_investment") or
                            init.portfolio <- add.constraint(portfolio = init.portfolio, type = "weight_sum", 
                                                       min_sum = 0.99, max_sum = 1.01) 
                            init.portfolio <- add.constraint(portfolio = init.portfolio, type = "long_only") 
                            
                            init.portfolio <- add.objective(portfolio=init.portfolio, type="return", name="mean")
                            optimized <- optimize.portfolio(R = AssetOptim, portfolio = init.portfolio, 
                                     optimize_method = "ROI",trace = TRUE, maxSR = TRUE,message = T)
                            out <- optimized[-2]
                            return(out)
                            }
                          
    numCores <- detectCores() 
    opt <- pbmcapply::pbmclapply(AssetsforOptimization,MaxMeanopt, mc.cores = numCores)
    weights <- lapply(opt, function(x){x$weights})
    weights <- Unequal_df(weights)
    Pweights <- list.append(Pweights, weights)
    Popt <- list.append(Popt, opt)
  
  }
  names(Pweights) <- c("P.R.MaxMean.Weights","P.C.MaxMean.Weights","E.R.MaxMean.Weights","E.C.MaxMean.Weights")
  names(Popt) <- c("P.R.MaxMean.Optimization","P.C.MaxMean.Optimization","E.R.MaxMean.Optimization",
                   "E.C.MaxMean.Optimization")
  
  PortfolioWeights[[PortType]][["MaxMean"]] <- Pweights
  PortfolioOptimization[[PortType]][["MaxMean"]] <- Popt
  
  rm(opt, weights, CopulaType, NoofRebalPeriod, AssetsforOptimization,simreturns,Pweights,Popt)

}
```


Part 5 : Proceed to Backtesting
