---
title: "4b Portfolio Optimization Conventional"
output: html_notebook
---

Here we optimize a portfolio Based on Conventional Assumptions.

1) Assume the Joint Dependence to be Normally Distributed.
2) Assume the Returns are Homoskedastic and their Residuals are not-autocorrelated. (Is this a fair Assumption?)
3) Calculate their Means, Covariances.
4) Create a Min Var, Min ES, Sharpe, Starr, and MaxMean Portfolio based on the above assumtption
5) I am using Parallel optimization




```{r, echo=FALSE}
library(fBasics)
library(readxl)
library(gdata)
library(PortfolioAnalytics)
library(PerformanceAnalytics)
library(ROI)
library(flextable)
library(officer)
library(dplyr)
library(gdata)
library(profvis)
library(tictoc)
library(rlist)
library(parallel)

```


Calculate the Means and Covariances.s

```{r}
MeanVarCorr <- list(Means = list(), Covariances = list(), Correlations = list())

for (PeriodNo in 1: length(SubFull)){
    
  MeanVarCorr[["Means"]][[PeriodNo]]  <- as.data.frame(colMeans(SubFull[[PeriodNo]]))
  colnames(MeanVarCorr[["Means"]][[PeriodNo]]) <- "Mean"
  MeanVarCorr[["Covariances"]][[PeriodNo]]  <- as.data.frame(cov(SubFull[[PeriodNo]]))  
   x <- as.data.frame(cor(SubFull[[PeriodNo]])) 
  x[upper.tri(x)]<-""
  MeanVarCorr[["Correlations"]][[PeriodNo]]  <- x
  rm(x)
}

rm(PeriodNo)
```

Initializing the variables -- Conventional PortfolioWeights and PortfolioOptimization.
```{r, echo=FALSE}

ConvPortfolioWeights <- list(Base = list(Naive = list(), MinSD = list(), MinES = list(), Sharpe = list(), Starr = list(), MaxMean = list()), Alt = list(Naive = list(), MinSD = list(), MinES = list(), Sharpe = list(), Starr = list(), MaxMean = list()))

ConvPortfolioOptimization <- list(Base = list(MinSD = list(), MinES = list(), Sharpe = list(), Starr = list(), MaxMean = list()), Alt = list(MinSD = list(), MinES = list(), Sharpe = list(), Starr = list(), MaxMean = list()))
```


```{r}
SubBase <- SubAlt <- list()
for (PeriodNo in 1:length(SubFull)){
  
  BN <- colnames(SubFull[[PeriodNo]])[colnames(SubFull[[PeriodNo]]) %in% AssetNames[["BaseNames"]]]
  AN <- colnames(SubFull[[PeriodNo]])[colnames(SubFull[[PeriodNo]]) %in% AssetNames[["AltNames"]]]
  SubBase[[PeriodNo]] <- SubFull[[PeriodNo]][,BN]
  SubAlt[[PeriodNo]] <- SubFull[[PeriodNo]][,AN] 
}
ConvPortfolio <- list(Base = SubBase, Alt = SubAlt)
rm(SubBase,SubAlt,AN,BN,PeriodNo)
```


1) 1/N or Naive Portfolio

```{r, echo=FALSE}
for(PortType in 1:2){
  
  if (length(ConvPortfolioWeights[[PortType]][["Naive"]]) != 0 ){ConvPortfolioWeights[[PortType]][["Naive"]] <- list()}
  
  originalreturns <- ConvPortfolio[[PortType]]
  Pweights <- list()
  
  
  AssetsforOptimization = originalreturns
  NoofRebalPeriod = length(AssetsforOptimization)
  
  weights <- list()
  
  for (PeriodNo in 1:NoofRebalPeriod){
    NoofAssets <- ncol(AssetsforOptimization[[PeriodNo]])
    
    Rownames <- colnames(AssetsforOptimization[[PeriodNo]])
    TempWeights <- as.numeric(rep(1/NoofAssets, each = NoofAssets))
    names(TempWeights) <- Rownames
    weights <- list.append(weights,TempWeights)
  }
  weights <- Unequal_df(weights)
  
  ConvPortfolioWeights[[PortType]][["Naive"]] <- weights
  
  rm(AssetsforOptimization, PeriodNo, NoofAssets, Rownames,TempWeights, weights, NoofRebalPeriod, originalreturns)
}
rm(PortType)
```


2) Min Std

```{r}
for(PortType in 1:2){
  tic(sprintf("PortType %d", PortType))
  if (length(ConvPortfolioWeights[[PortType]][["MinSD"]]) != 0 )
    {ConvPortfolioWeights[[PortType]][["MinSD"]] <- list()}
  
  originalreturns <- ConvPortfolio[[PortType]]
  Pweights <- list()
  
  
  AssetsforOptimization <- originalreturns
  NoofRebalPeriod <- length(AssetsforOptimization)
  
  weights <- opt <- list()
  
   MinSDOpt <- function(AssetOptim){
                      init.portfolio <- portfolio.spec(assets = colnames(AssetOptim))
                      #init.portfolio <- add.constraint(portfolio = init.portfolio, type =
                      #                                  "full_investment") or
                      init.portfolio <- add.constraint(portfolio = init.portfolio, type = "weight_sum", 
                                               min_sum = 0.99, max_sum = 1.01) 
                      init.portfolio <- add.constraint(portfolio = init.portfolio, type = 
                      "long_only")
                      init.portfolio <- add.objective(portfolio=init.portfolio, type="risk", name="var")
                      optimized <- optimize.portfolio(R = AssetOptim, portfolio = init.portfolio, 
                                       optimize_method = "ROI",trace = TRUE,message = T)
                      out <- optimized[-2]
                      return(out)
    }
    
    numCores <- detectCores() 
    opt <- parallel::mclapply(AssetsforOptimization,MinSDOpt, mc.cores = numCores)
    weights <- lapply(opt, function(x){x$weights})
  
  
    weights <- Unequal_df(weights)  
    ConvPortfolioWeights[[PortType]][["MinSD"]] <- weights
    ConvPortfolioOptimization[[PortType]][["MinSD"]] <- opt
    rm(opt, weights, NoofRebalPeriod, PeriodNo, init.portfolio, AssetsforOptimization,originalreturns)
    toc()
}

rm(PortType)
```


3) Min ES

```{r}
for(PortType in 1:2){
  tic(sprintf("PortType %d", PortType))
  if (length(ConvPortfolioWeights[[PortType]][["MinES"]]) != 0 ){ConvPortfolioWeights[[PortType]][["MinES"]] <- list()}
  
  originalreturns <- ConvPortfolio[[PortType]]
  Pweights <- list()
  
  
  AssetsforOptimization = originalreturns
  NoofRebalPeriod = length(AssetsforOptimization)
  
  weights <- opt <- list()
  
  
  MinESopt <- function(AssetOptim){
                         init.portfolio <- portfolio.spec(assets = colnames(AssetOptim))
                        #init.portfolio <- add.constraint(portfolio = init.portfolio, type =
                        #                                  "full_investment") or
                        init.portfolio <- add.constraint(portfolio = init.portfolio, type = "weight_sum", 
                                               min_sum = 0.99, max_sum = 1.01) 
                        init.portfolio <- add.constraint(portfolio = init.portfolio, type = 
                        "long_only")
              
              init.portfolio <- add.objective(portfolio=init.portfolio, type="risk", name="ES")
              optimized <- optimize.portfolio(R = AssetOptim, portfolio = init.portfolio, 
                       optimize_method = "ROI",trace = TRUE,message = T)
              out <- optimized[-2]
              return(out)
              }
  numCores <- detectCores() 
  opt <- parallel::mclapply(AssetsforOptimization,MinESopt, mc.cores = numCores)
  weights <- lapply(opt, function(x){x$weights})
  
  weights <- Unequal_df(weights)  
  ConvPortfolioWeights[[PortType]][["MinES"]] <- weights
  ConvPortfolioOptimization[[PortType]][["MinES"]] <- opt
  rm(opt, weights, NoofRebalPeriod, PeriodNo, init.portfolio, AssetsforOptimization,originalreturns)
  toc()
}

rm(PortType)
```

4) Sharpe Portfolio

```{r}
for(PortType in 1:2){
  tic(sprintf("PortType %d", PortType))
  if (length(ConvPortfolioWeights[[PortType]][["Sharpe"]]) != 0 ){ConvPortfolioWeights[[PortType]][["Sharpe"]] <-
    list()}
  
  originalreturns <- ConvPortfolio[[PortType]]
  Pweights <- list()
  AssetsforOptimization = originalreturns
  NoofRebalPeriod = length(AssetsforOptimization)
  
  weights <- opt <- list()
  
  
   Sharpeopt <- function(AssetOptim){
                init.portfolio <- portfolio.spec(assets = colnames(AssetOptim))
                 #init.portfolio <- add.constraint(portfolio = init.portfolio, type =
                        #                                  "full_investment") or
                        init.portfolio <- add.constraint(portfolio = init.portfolio, type = "weight_sum", 
                                               min_sum = 0.99, max_sum = 1.01) 
                        init.portfolio <- add.constraint(portfolio = init.portfolio, type = 
                        "long_only") 
                init.portfolio <- add.objective(portfolio=init.portfolio,type="return", name="mean")
                init.portfolio <- add.objective(portfolio=init.portfolio,type="risk", name="StdDev")
                optimized <- optimize.portfolio(R = AssetOptim, portfolio = init.portfolio, 
                         optimize_method = "ROI",trace = TRUE, maxSR = TRUE,message = T)
                out <- optimized[-2]
                return(out)
                }
    numCores <- detectCores() 
    opt <- parallel::mclapply(AssetsforOptimization,Sharpeopt, mc.cores = numCores)
    weights <- lapply(opt, function(x){x$weights})
  
  
  
    weights <- Unequal_df(weights)  
    ConvPortfolioWeights[[PortType]][["Sharpe"]] <- weights
    ConvPortfolioOptimization[[PortType]][["Sharpe"]] <- opt
    rm(opt, weights, NoofRebalPeriod, PeriodNo, init.portfolio, AssetsforOptimization,originalreturns)
    toc()
}

rm(PortType)
```

5) Starr Portfolio

```{r}
for(PortType in 1:2){
  tic(sprintf("PortType %d", PortType))
  if (length(ConvPortfolioWeights[[PortType]][["Starr"]]) != 0 ){ConvPortfolioWeights[[PortType]][["Starr"]] <- list()}
  
  originalreturns <- ConvPortfolio[[PortType]]
  Pweights <- list()
  
  
  AssetsforOptimization = originalreturns
  NoofRebalPeriod = length(AssetsforOptimization)
  
  weights <- opt <- list()
  
  Staropt <- function(AssetOptim){
                        init.portfolio <- portfolio.spec(assets = colnames(AssetOptim))
                         #init.portfolio <- add.constraint(portfolio = init.portfolio, type =
                        #                                  "full_investment") or
                        init.portfolio <- add.constraint(portfolio = init.portfolio, type = "weight_sum", 
                                               min_sum = 0.99, max_sum = 1.01) 
                        init.portfolio <- add.constraint(portfolio = init.portfolio, type = 
                        "long_only") 
                        init.portfolio <- add.objective(portfolio=init.portfolio, type="risk", name="ES")
                        init.portfolio <- add.objective(portfolio=init.portfolio, type="return", name="mean")
                        optimized <- optimize.portfolio(R = AssetOptim, portfolio = init.portfolio, 
                                 optimize_method = "ROI",trace = TRUE, maxSR = TRUE,message = T)
                        out <- optimized[-2]
                        return(out)
                        }
  numCores <- detectCores() 
  opt <- parallel::mclapply(AssetsforOptimization,Staropt, mc.cores = numCores)
  weights <- lapply(opt, function(x){x$weights})

  weights <- Unequal_df(weights)  
  ConvPortfolioWeights[[PortType]][["Starr"]] <- weights
  ConvPortfolioOptimization[[PortType]][["Starr"]] <- opt
  rm(opt, weights, NoofRebalPeriod, PeriodNo, init.portfolio, AssetsforOptimization,originalreturns)
  toc()
}

rm(PortType)
```



6) MaxMean

```{r}
for(PortType in 1:2){
  tic(sprintf("PortType %d", PortType))
  if (length(ConvPortfolioWeights[[PortType]][["MaxMean"]]) != 0 ){ConvPortfolioWeights[[PortType]][["MaxMean"]] <-
    list()}
  
  originalreturns <- ConvPortfolio[[PortType]]
  Pweights <- list()
  
  
  AssetsforOptimization = originalreturns
  NoofRebalPeriod = length(AssetsforOptimization)
  
  weights <- opt <- list()
 
  
 MaxMeanopt <- function(AssetOptim){
                        init.portfolio <- portfolio.spec(assets = colnames(AssetOptim))
                        #init.portfolio <- add.constraint(portfolio = init.portfolio, type =
                        #                                  "full_investment") or
                        init.portfolio <- add.constraint(portfolio = init.portfolio, type = "weight_sum", 
                                               min_sum = 0.99, max_sum = 1.01) 
                        init.portfolio <- add.constraint(portfolio = init.portfolio, type = 
                        "long_only") 
                        init.portfolio <- add.objective(portfolio=init.portfolio, type="return", name="mean")
                        optimized <- optimize.portfolio(R = AssetOptim, portfolio = init.portfolio, 
                                 optimize_method = "ROI",trace = TRUE,message = T)
                        out <- optimized[-2]
                        return(out)
                        }
                          
  numCores <- detectCores() 
  opt <- parallel::mclapply(AssetsforOptimization,MaxMeanopt, mc.cores = numCores)
  weights <- lapply(opt, function(x){x$weights})
  
  weights <- Unequal_df(weights)  
  ConvPortfolioWeights[[PortType]][["MaxMean"]] <- weights
  ConvPortfolioOptimization[[PortType]][["MaxMean"]] <- opt
  rm(opt, weights, NoofRebalPeriod, PeriodNo, init.portfolio, AssetsforOptimization,originalreturns)
  toc()
}

rm(PortType)
```


Part 5b: Back testing
