---
title: "5 Backtesting"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

For Backtesting we follow the below steps:

1) Compare Base, Alternative and Sp500 Return performance
   For the Performance Metrics of the three portfolios, we use the below indicators
    i) Evolution over the investment period
   ii) Annualized Mean
   iii) Annualized Standard Deviation 
   iv) Compounded Annual Growth Rate (CAGR)
   
2) Weights Graph of Cryptocurrencies for each period 

All the above is carried on a combination of the below for Base and Alternative Portfolio:

Distribution and Copula Type  | Optimization  
----------------------------- | ------------------
Parametric and R Vine Copula  |  Min.Var      
Parametric and C Vine Copula  |  Min.ES        
Empirical  and R Vine Copula  |  Sharpe        
Empirical  and C Vine Copula  |  Starr and MaxMean 

```{r, echo=FALSE}
library(fBasics)
library(readxl)
library(gdata)
library(PortfolioAnalytics)
library(PerformanceAnalytics)
library(ROI)
library(flextable)
library(officer)
library(dplyr)
library(gdata)
library(profvis)
library(tictoc)
library(xts)
library(rlist)
```



```{r}
SubFullBackTesting <- Commodities[["SubFullBackTesting"]]
prices <- Commodities[["prices"]]
PortfolioWeights <- Commodities[["PortfolioWeights"]]

PortfolioWeights[["Base"]][["Starr"]] <- PortfolioWeights[["Alt"]][["Starr"]] <- NULL #Not considering STARR Portfolio Optimization
``` 

Market Portfolio (SP500)
 
```{r}
library(PerformanceAnalytics)
NoofRebalancingPeriod <- length(SubFullBackTesting)

MarketIndex <- "SP500"
MarketPort <-  prices %>% select(c(eval(MarketIndex))) %>%  as.xts(order.by = prices[,1]) %>% na.omit %>% Return.calculate(method = "log") %>% na.omit
rm(MarketIndex)

library(rlist)
SubMarketPort <- list()
for (PeriodNo in 1:length(SubFullBackTesting)){
   TempDate <- index(SubFullBackTesting[[PeriodNo]])   
   SubMarketPort[[PeriodNo]] <-  MarketPort[paste(TempDate[1],"/",
                                                  TempDate[500],sep=""),]
}

#Extracting the Returns for the last 30 days of each Investment period

multiple.fun <- function(x){
    Dt <- xts::last(x) %>% index %>% as.Date}

a<- lapply(SubMarketPort, multiple.fun)
a<- Reduce(c,a)
MarketReturns <- as.data.frame(matrix(nrow = NoofRebalancingPeriod, ncol = 2))
for(PeriodNo in 1:NoofRebalancingPeriod){
   MarketReturns[PeriodNo,2] <- xts::last(SubMarketPort[[PeriodNo]], n = 30) %>% colSums() %>% expm1() #Converting ln(r) to arithematic
   MarketReturns[PeriodNo,1] <- as.character(a[[PeriodNo]])
}

MarketReturns<- as.xts(MarketReturns[,-1], order.by = as.Date(MarketReturns[,1]))
MarketReturns <- MarketReturns[-1,]
MR <- xts(x = 0, order.by = as.Date("2015-04-29"))
#xts(x = t(rep(0,ncol(PortfolioReturns[[PortType]]))), order.by = as.Date("2015-04-29"))
names(MR) <- names(MarketReturns) <- "SP500"
MR <- rbind.xts(MR, MarketReturns)

MarketEvolution <- cumprod(MR+1)
names(MarketEvolution) <- "SP500"

rm(a, PeriodNo, NoofRebalancingPeriod, MR, TempDate)

```

FullPort

```{r}
NoofRebalancingPeriod <- length(SubFullBackTesting)
NoofAssets <- ncol(SubFullBackTesting[[NoofRebalancingPeriod]])

a<- lapply(SubFullBackTesting, multiple.fun)
a<- Reduce(c,a)

AssetReturns <- as.data.frame(matrix(nrow = NoofRebalancingPeriod, ncol = NoofAssets, dimnames = list(NULL,colnames(SubFullBackTesting[[NoofRebalancingPeriod]]))))

TempDate <- matrix(matrix(nrow = NoofRebalancingPeriod, ncol = 1))

for(PeriodNo in 1:NoofRebalancingPeriod){
   AssetReturns[PeriodNo,colnames(SubFullBackTesting[[PeriodNo]])] <-
      xts::last(SubFullBackTesting[[PeriodNo]],n = 30) %>% colSums() %>% expm1() #Converting ln(r) to arithematic
   TempDate[PeriodNo,] <- as.character(a[[PeriodNo]])
}

AssetReturns <- as.xts(AssetReturns, order.by = as.Date(TempDate))


rm(a,NoofRebalancingPeriod,NoofAssets)

```

DateStamp the Portfolio Weights

```{r}
for (PortType in 1:2){
   for (OptimizationType in 1:5){
      

      for(Copula in 1:4){
      
         PortfolioWeights[[PortType]][[OptimizationType]][[Copula]] <- 
            as.xts(PortfolioWeights[[PortType]][[OptimizationType]][[Copula]], order.by = as.Date(TempDate))
     }
      }
   }


rm(PortType,OptimizationType,Copula)
```



Creating Portfolio Returns and Evolution

Initializing the variables -- PortfolioReturns and Evolution
```{r, echo=FALSE}

PortfolioReturns <- list(Base = list(NaivePortfolio = list(), MinSD = list(), MinES = list(), Sharpe = list(),  MaxMean = list()), Alt = list(NaivePortfolio = list(), MinSD = list(), MinES = list(), Sharpe = list(), MaxMean = list()))

PortfolioEvolution <- list(Base = list(), Alt = list())
```

```{r}

for (PortType in 1:2){

   for (OptimizationType in 1:5){
   

   Copulas <- list()
   
      for(Copula in 1:4){
         a <- lag.xts(PortfolioWeights[[PortType]][[OptimizationType]][[Copula]])
         a <- a[-1,]
         
         TempCop <- a * AssetReturns[, colnames(a)]
         c <- index(TempCop)
         Temp <- as.xts(rowSums(TempCop, na.rm = TRUE), order.by = c)
     
         Copulas <- list.append(Copulas, Temp)
         rm(TempCop, Temp,a)
      }
      names(Copulas) <- names(PortfolioWeights[[PortType]][[OptimizationType]])
      PortfolioReturns[[PortType]][[OptimizationType]] <-   Copulas
      PortfolioReturns[[PortType]][[OptimizationType]] <-    
         sapply(PortfolioReturns[[PortType]][[OptimizationType]],unlist)
    PortfolioReturns[[PortType]][[OptimizationType]] <- as.xts(PortfolioReturns[[PortType]][[OptimizationType]], 
                                                               order.by = c)
    colnames(PortfolioReturns[[PortType]][[OptimizationType]]) <- gsub(x =                                                               colnames(PortfolioReturns[[PortType]][[OptimizationType]]), "Weights","Returns")
    rm(c)
      }
   PortfolioReturns[[PortType]]<- do.call(cbind,PortfolioReturns[[PortType]])
   z<- xts(x = t(rep(0,ncol(PortfolioReturns[[PortType]]))), order.by = as.Date("2015-04-29")) # Don't forget to change the first investment date from 2015-04-29 
   colnames(z) <- colnames(PortfolioReturns[[PortType]])
   z <- rbind.xts(z,PortfolioReturns[[PortType]]) 
   PortfolioEvolution[[PortType]] <-  cumprod(z+1)
   rm(z)
}

rm(Copula,OptimizationType,PortType)
```


Calculating Annualized Returns, Standard Deviation and CAGR of the Portfolios

Annualized Returns and Std Deviation ---- Returns

CAGR ---- Evolution

```{r}
pfactor <- 252/30

   PerformanceMetrics <- list()
   for(PortType in 1:2){
      
      Evolution <- merge.xts(MarketEvolution,PortfolioEvolution[[PortType]])
      Returns <- merge.xts(MarketReturns,PortfolioReturns[[PortType]])
      
      CAGR <- Evolution[nrow(Evolution),]^(pfactor/(nrow(Evolution)-1)) - 1
      CAGR <- setNames(as.numeric(CAGR), colnames(CAGR))
      MEAN <- colMeans(Returns)*pfactor
      STD <- colStdevs(Returns)*sqrt(pfactor)
      
      g <- cbind(MEAN,STD,CAGR)
      PerformanceMetrics[[PortType]] <- t(g)
      
      rm(Evolution, Returns, CAGR, MEAN, STD,g)
   }
   
   names(PerformanceMetrics) <- c("Base","Alt")
   
rm(pfactor, PortType)   
```



```{r}

Commodities[["Backtesting"]] <- list.append(Commodities[["Backtesting"]],PerformanceMetrics = PerformanceMetrics, PortfolioEvolution = PortfolioEvolution, PortfolioReturns = PortfolioReturns, PortfolioWeights = PortfolioWeights)

rm(PerformanceMetrics,PortfolioEvolution,MarketEvolution,PortfolioReturns,MarketReturns, MarketPort, SubMarketPort)
rm(TempDate, Copulas, PeriodNo, AssetReturns)
rm(SubFullBackTesting,prices,PortfolioWeights)
```



Part 6: Report Generation and such




