---
title: "R Notebook"
output: html_notebook
---

```{r}
library(ggpubr)
```


Creating a mega xts object consisting of Evolution  and weight columns for all the five different portfolios separately.

A Name would be a combination of the below:

Portfolio = Commo,Fixed,MarFixCom,Market,Sector
Dependence = Conventional, Copula 
Copula Type = NaN, P.R, P.C, E.R, E.C
Base/Alt  = Base, Alt
Optimization = Naive, MinSD, MinES, Sharpe, MaxMean

Portfolio * Dependence * Copula Type * Base/Alt * Optimization 

5*2*5*2*5 = 500 columns and 41 rows (for 41 time periods)

```{r}


a <- Sectors[["Backtesting"]][["ConvPortfolioEvolution"]] 


for ( i  in 1:2){
  colnames(a[[i]]) <- paste("Sector","Copula",names(a)[i],colnames(a[[i]]) ,sep = ".")
}

Sectors[["Backtesting"]][["ConvPortfolioEvolution"]]  <- NULL

Sectors[["Backtesting"]]  <- list.append(Sectors[["Backtesting"]], PortfolioEvolution = a)

rm(a,i)
```


```{r}

a <- Sectors[["Backtesting"]][["PortfolioEvolution"]] 


for ( i  in 1:2){
  colnames(a[[i]]) <- gsub(colnames(a[[i]]), pattern = "Returns", replacement = "Evolution")
  colnames(a[[i]]) <- paste("Sector","Copula",names(a)[i],colnames(a[[i]]) ,sep = ".")
}

Sectors[["Backtesting"]][["PortfolioEvolution"]]  <- NULL

Sectors[["Backtesting"]]  <- list.append(Sectors[["Backtesting"]], PortfolioEvolution = a)

rm(a,i)


```

Weights

Portfolio * Dependence * Copula Type * Base/Alt * Optimization  * AssetName
```{r}

a <- Sectors[["Backtesting"]][["ConvPortfolioWeights"]]

for (BorA in 1:2){
  for(PortOpt in 1:6){
     
    colnames(a[[BorA]][[PortOpt]]) <- paste("Sector","Conv","NaN",names(a)[BorA], names(a[[BorA]])[PortOpt],colnames(a[[BorA]][[PortOpt]]),"Weights", sep = ".")
    
    
  }
}

Sectors[["Backtesting"]][["ConvPortfolioWeights"]] <- NULL

Sectors[["Backtesting"]] <- list.append(Sectors[["Backtesting"]],ConvPortfolioWeights = a )

rm(a,BorA, PortOpt)

```


```{r}
a <- Sectors[["Backtesting"]][["PortfolioWeights"]]


for (BorA in 1:2){
    for(Portopt in 1:5){
      for(Cop in 1:4){
        
        colnames(a[[BorA]][[Portopt]][[Cop]]) <- paste("Sector","Copula", names(a)[BorA],
                                                       names(a[[BorA]][[Portopt]])[Cop], 
                                                       colnames(a[[BorA]][[Portopt]][[Cop]]),sep = ".")
    }
  }
}

Sectors[["Backtesting"]][["PortfolioWeights"]] <- NULL

Sectors[["Backtesting"]] <- list.append(Sectors[["Backtesting"]] ,PortfolioWeights = a)


rm(BorA, Cop, Portopt, a)
```


Merging Evolution and Weights

```{r}
a <- Sectors[["Backtesting"]][["ConvPortfolioEvolution"]]
b <- Sectors[["Backtesting"]][["PortfolioEvolution"]]
c <- Sectors[["Backtesting"]][["MarketEvolution"]]
d <- Sectors[["Backtesting"]][["ConvPortfolioWeights"]]
e <- Sectors[["Backtesting"]][["PortfolioWeights"]]


### $$$$$$$ ************************************************
MergeEvolution <- merge.xts(a[[1]],a[[2]],b[[1]],b[[2]],c)


  MergeWeights <- NULL
for(BorA in 1:2){
  for(Portopt in 1:6){
    
    MergeWeights <- merge.xts(MergeWeights,d[[BorA]][[Portopt]])
  }
}  

 for(BorA in 1:2){
  for(Portopt in 1:5){
    for(Cop in 1:4){
MergeWeights <- merge.xts(MergeWeights,e[[BorA]][[Portopt]][[Cop]])
  }
  }   
 }
EvolutionandWeights <- merge.xts(MergeEvolution,MergeWeights)
  
### $$$$$$$ ******************************************************
Sectors[["Backtesting"]] <- list.append(Sectors[["Backtesting"]], Sector.EvolutionandWeights = EvolutionandWeights)

rm(a,b,c,d,e,MergeEvolution,MergeWeights,EvolutionandWeights,BorA, Portopt, Cop)
```

Performance Metrics:

Portfolio * Dependence * Copula Type * Base/Alt * Optimization  *


```{r}

a <- Sectors[["Backtesting"]][["ConvPerformanceMetrics"]] 
b <- Sectors[["Backtesting"]][["PerformanceMetrics"]]

for(BorA in 1:2){
colnames(a[[BorA]])[-1] <- paste("Sector","Conv","-", names(a)[BorA],colnames(a[[BorA]])[-1],sep = ".")
colnames(b[[BorA]])[-1] <- gsub(colnames(b[[BorA]])[-1], pattern = ".Returns", replacement = "")
colnames(b[[BorA]])[-1] <- paste("Sector","Copula", names(b)[BorA],colnames(b[[BorA]])[-1],sep = ".")
}

c = cbind(as.data.frame((a[[1]])),as.data.frame((a[[2]])),as.data.frame((b[[1]])),as.data.frame((b[[2]])))

c = subset(c , select = which(!duplicated(colnames(c))))

Sectors[["Backtesting"]] <- list.append(Sectors[["Backtesting"]], Sector.AllPerformanceMetrics = t(c))


rm(a,b,c,BorA)


```

```{r}



EvolutionAndWeights <- list(Commo = Commodities[[6]][[11]],Fixed = FixedIncome[[6]][[11]],
                            MarFixCom = MarketFixedCommodities[[6]][[11]], Market = MarketIndices[[6]][[11]],
                            Sector = Sectors[[6]][[11]]
                            )

PerformanceM <- list(Commo = Commodities[[6]][[12]],Fixed = FixedIncome[[6]][[12]],
                     MarFixCom = MarketFixedCommodities[[6]][[12]], Market = MarketIndices[[6]][[12]],
                     Sector = Sectors[[6]][[12]], 
                     Alltogether = rbind(Commodities[[6]][[12]],FixedIncome[[6]][[12]],
                                         MarketFixedCommodities[[6]][[12]],
                                         MarketIndices[[6]][[12]],Sectors[[6]][[12]])
                       
                            )

```

Xts to Data frame

```{r}
for (i in 1:length(EvolutionAndWeights)){
EvolutionAndWeights[[i]] <- data.frame(Date = index(EvolutionAndWeights[[i]]), coredata(EvolutionAndWeights[[i]]))
}
```

#########################   THe Graphing Starts Here ###################

Create a Matrix of Performance M in Excel


Creating Portfolio wise plots

DrawnDown
```{r}
library(PerformanceAnalytics)
library(dplyr)

a <- EvolutionAndWeights[["Commo"]] %>% select(Date, intersect(intersect(contains("Evolution"), contains("Alt")), contains(c("Naive","MinSD","MinES","Sharpe","MaxMean"))))

ret <- data.frame(matrix(data = NA, nrow = nrow(a), ncol = ncol(a)))

colnames(ret) <- colnames(a)

ret[,1] <- a[,1]

for(i in 2:41){
  ret[i,2:ncol(a)] <- (a[i,2:ncol(a)]/a[i-1,2:ncol(a)])-1
}


Optimization <- c("Naive","MinSD","MinES","Sharpe","MaxMean")
Copula <- c("Conv","P-R","P-C","E-R","E-C")

for (i in 1:5){
dd <- ret %>% select(Date, contains(Copula[i])) %>% na.omit() 
dd <- as.xts(dd[,-1], order.by = dd[,1])
colnames(dd) <- c("Naive","MinSD","MinES","Sharpe","MaxMean")

}
#chart.Drawdown(dd, legend.loc = "bottomleft", plot.engine = "ggplot2") # Need to find a way to get it grey sclaed



```

Chart Evolution Optimization and Copulwise for Alternative Portfolios

Commodities
```{r}

a <- EvolutionAndWeights[["AlltogetherLong"]] %>% filter(Portfolio == "Sector", EorW == "Evolution", BorA == "Alt", Opt != "Starr")

b <- ggplot(a, aes(x = Date,y = value, linetype = Opt, group = Opt)) + geom_line() + facet_wrap(~VineType, scales = "free_y") + xlab("") + ylab("Evolution (in $)") + theme_classic() + theme(strip.background = element_blank(), legend.position = c(0.8,0.2)) +labs(linetype ="Optimization")

c <- ggplot(a, aes(x = Date,y = value, linetype = VineType, group =VineType)) + geom_line() + facet_wrap(~Opt, scales = "free_y")+ xlab("") +  ylab("Evolution (in $)") + theme_classic() + theme(strip.background = element_blank(), legend.position = c(0.8,0.2)) +labs(linetype ="Dependence")

ggsave("Sector3.pdf",plot = b, width = 10, height = 6)
ggsave("Sector4.pdf",plot = c, width = 10, height = 6)
rm(a)
```

Fixed
```{r}

a <- EvolutionAndWeights[["AlltogetherLong"]] %>% filter(Portfolio == "Fixed", EorW == "Evolution", BorA == "Alt", Opt != "Starr")

b<- ggplot(a, aes(x = Date,y = value, linetype = Opt, group = Opt)) + geom_line() + facet_wrap(~VineType, scales = "free_y") + xlab("") + ylab("Evolution (in $)") + theme_classic() + theme(strip.background = element_blank(), legend.position = c(0.8,0.2)) +labs(linetype ="Optimization")

c <- ggplot(a, aes(x = Date,y = value, linetype = VineType, group =VineType)) + geom_line() + facet_wrap(~Opt, scales = "free_y")+ xlab("") + ylab("Evolution (in $)") + theme_classic() + theme(strip.background = element_blank(), legend.position = c(0.8,0.2)) +labs(linetype ="Dependence")
rm(a)
```



Sector
```{r}

a <- EvolutionAndWeights[["AlltogetherLong"]] %>% filter(Portfolio == "Sector", EorW == "Evolution", BorA == "Alt", Opt != "Starr")

b <- ggplot(a, aes(x = Date,y = value, linetype = Opt, group = Opt)) + geom_line() + facet_wrap(~VineType, scales = "free_y") + xlab("") + ylab("Evolution (in $)") + theme_classic() + theme(strip.background = element_blank(), legend.position = c(0.8,0.2)) +labs(linetype ="Optimization")

c <- ggplot(a, aes(x = Date,y = value, linetype = VineType, group =VineType)) + geom_line() + facet_wrap(~Opt, scales = "free_y") + xlab("")+ ylab("Evolution (in $)") + theme_classic() + theme(strip.background = element_blank(), legend.position = c(0.8,0.2)) +labs(linetype ="Dependence")
rm(a)
```

Market
```{r}

a <- EvolutionAndWeights[["AlltogetherLong"]] %>% filter(Portfolio == "Market", EorW == "Evolution", BorA == "Alt", Opt != "Starr")

b<- ggplot(a, aes(x = Date,y = value, linetype = Opt, group = Opt)) + geom_line() + facet_wrap(~VineType, scales = "free_y") + xlab("") + ylab("Evolution (in $)") + theme_classic() + theme(strip.background = element_blank(), legend.position = c(0.8,0.2)) +labs(linetype ="Optimization")

c <- ggplot(a, aes(x = Date,y = value, linetype = VineType, group =VineType)) + geom_line() + facet_wrap(~Opt, scales = "free_y")+ xlab("") + ylab("Evolution (in $)") + theme_classic() + theme(strip.background = element_blank(), legend.position = c(0.8,0.2)) +labs(linetype ="Dependence")
rm(a)
```


Market Fixed and Commodities
```{r}

a <- EvolutionAndWeights[["AlltogetherLong"]] %>% filter(Portfolio == "MarFixCom", EorW == "Evolution", BorA == "Alt", Opt != "Starr")

b <- ggplot(a, aes(x = Date,y = value, linetype = Opt, group = Opt)) + geom_line() + facet_wrap(~VineType, scales = "free_y") + xlab("") + ylab("Evolution (in $)") + theme_classic() + theme(strip.background = element_blank(), legend.position = c(0.8,0.2)) +labs(linetype ="Optimization")

c <- ggplot(a, aes(x = Date,y = value, linetype = VineType, group =VineType)) + geom_line() + facet_wrap(~Opt, scales = "free_y")+ xlab("") + ylab("Evolution (in $)") + theme_classic() + theme(strip.background = element_blank(), legend.position = c(0.8,0.2)) +labs(linetype ="Dependence")
rm(a)
```


Weights



```{r}
a <- EvolutionAndWeights[["AlltogetherLong"]] %>% filter(Portfolio == "Market", EorW == "Weights", BorA == "Alt", Opt != "Starr", Opt != "Naive", Asset %in% c("BTC","LTC","XRP","ETH"))

g1 <- ggplot(a, aes(x = Date,y = value, linetype = VineType, group =VineType)) + geom_line()  + facet_wrap(Asset~Opt, scales = "free_y")+ xlab("") + ylab("Weights") + theme_classic() + theme(strip.background = element_blank(),strip.text = element_blank(), legend.position = "bottom") +labs(linetype ="Dependence")

g2 <- ggplot(a, aes(x = Date,y = value, linetype = VineType, group =VineType)) + geom_line()  + facet_grid(Asset~Opt, scales = "free_y")+ xlab("") + ylab("Weights") + theme_classic() + theme(strip.background = element_blank()) +labs(linetype ="Dependence")


library(grid)
library(gtable) 
gt1 = ggplot_gtable(ggplot_build(g1))
gt2 = ggplot_gtable(ggplot_build(g2))
gt1$grobs[grep('strip-t.+1$', gt1$layout$name)] = gt2$grobs[grep('strip-t', gt2$layout$name)]
grid.draw(gt1)

gt.side1 = gtable_filter(gt2,'strip-r-1')
gt.side2 = gtable_filter(gt2,'strip-r-2')
gt.side3 = gtable_filter(gt2,'strip-r-3')
gt.side4 = gtable_filter(gt2,'strip-r-4')

gt1 = gtable_add_cols(gt1, widths=gt.side1$widths[1], pos = -1)
gt1 = gtable_add_grob(gt1, zeroGrob(), t = 1, l = ncol(gt1), b=nrow(gt1))

panel_id <- gt1$layout[grep('panel-.+1$', gt1$layout$name),]
gt1 = gtable_add_grob(gt1, gt.side1, t = panel_id$t[1], l = ncol(gt1))
gt1 = gtable_add_grob(gt1, gt.side2, t = panel_id$t[2], l = ncol(gt1))
gt1 = gtable_add_grob(gt1, gt.side3, t = panel_id$t[3], l = ncol(gt1))
gt1 = gtable_add_grob(gt1, gt.side4, t = panel_id$t[4], l = ncol(gt1))

grid.newpage()
grid.draw(gt1)
ggsave("Marketweight.pdf",plot = gt1, width = 10, height = 10)

```
Box Plot

```{r}
 a<- EvolutionAndWeights[["PortfolioReturnsLong"]] %>% filter(BorA == "Alt", Portfolio == "Commo", Opt != "Starr")
 
  b <- unite(a,VineType, Opt, col = "VineOpt", sep = "_")
  
  c <- cbind(a,VineOpt = b[,5])

d <- ggplot(c,aes(x = value, y = VineType)) + geom_boxplot(alpha = 0.3, lwd = 0.2) + facet_wrap(~Opt)+ ylab("Dependence") + xlab("Returns") + theme_classic() + theme(strip.background = element_blank()) + geom_jitter(alpha = 0.3)

e <- ggplot(c,aes(x = value, y = Opt)) + geom_boxplot(alpha = 0.3, lwd = 0.2) + facet_wrap(~VineType, scales = "free")+ ylab("Optimization") + xlab("Returns") + theme_classic() + theme(strip.background = element_blank()) + geom_jitter(alpha = 0.3)



ggsave("CommoBox1.pdf",plot = d, width = 8, height = 4)
ggsave("CommoBox2.pdf",plot = e, width = 8, height = 4)
```


For Motivational purposes I show the 

1) Cryptocurrency and Bitcoin Market Cap evolution.
2) Four cryptocurrencies - Price, Volume and Return Evolution.
3) BoxPlots for all the assets returns to show the variance. 


Extracting Cryptocurrency prices
```{r}
library(crypto) #fdownloading cryptocurrency prices from coinmarketcap.com
library(reshape2) 
library(xts)
library(PerformanceAnalytics)
library(dplyr)
library(tidyverse)

CryptoPrices <- crypto_history(coin = c("ETH", "XRP","BTC",
                                        "LTC")
                                        )
CryptoPrices <- CryptoPrices[,c("symbol","date","close", "volume")]

CryptoPrices$volume <- CryptoPrices$volume/1000000000


colnames(CryptoPrices) <- c("Symbol","Date","Price","Volume") 



BTC <- CryptoPrices %>% filter(Symbol == "BTC")
LTC <- CryptoPrices %>% filter(Symbol == "LTC")
XRP <- CryptoPrices %>% filter(Symbol == "XRP")
ETH <- CryptoPrices %>% filter(Symbol == "ETH")

BTC$Return <- Return.calculate(as.xts(BTC$Price, order.by = BTC$Date))
LTC$Return <- Return.calculate(as.xts(LTC$Price, order.by = LTC$Date))
XRP$Return <- Return.calculate(as.xts(XRP$Price, order.by = XRP$Date))
ETH$Return <- Return.calculate(as.xts(ETH$Price, order.by = ETH$Date))


a<- rbind(BTC,ETH,XRP,LTC)

CryptoPrices <- a

rm(BTC,LTC,XRP,ETH,a)

```


2)

```{r}
library(gtable)
library(grid)
library(ggplotify)

crypto <- "ETH"

a <- ggplotGrob(ggplot(data = CryptoPrices %>% filter(Symbol == crypto), aes(x=Date, y = Price)) + geom_line(color = "#1B9E77") + xlab("")  + theme_classic() + theme(axis.text.x = element_blank(),axis.ticks.x = element_blank(), axis.ticks.length =unit(.10, "cm")) + ylab("") + ggtitle("ETH") + theme(plot.margin=unit(c(0.1,0,0,0),"cm"), plot.title = element_text(hjust = 0.5, size = 15))) 

b <- ggplotGrob(ggplot(data = CryptoPrices %>% filter(Symbol == crypto), aes(x=Date, y = Volume)) + geom_area(fill = "#E6AB02", alpha = 0.5) + xlab("")  + theme_classic()  + theme(axis.text.x = element_blank(),axis.ticks.x = element_blank())  + ylab("") +theme(plot.margin=unit(c(0,0,0,0),"mm")))

c <- ggplotGrob(ggplot(data = CryptoPrices %>% filter(Symbol == crypto), aes(x=Date, y = Return)) + geom_line(color = "#7570B3") + xlab("")+ theme_classic() + ylab("")+theme(plot.margin=unit(c(0,0,0,0),"mm")))

g <- rbind(a,b,c, size = "first")

g$widths <- unit.pmax(a$widths, b$widths, c$widths)

a <-as.ggplot(g)

ggsave('ETH.pdf', a, height = 5, width = 6)


```


3) 

```{r}
a <- prices[,c("Dates","SP500","DJIA","NASDAQ","IT","ENERGY","HEALTH","UTILITY","FINANCIAL","CONSD","CONSS","COMM","INDUS","REAL","MATERIAL","GOLD","SILVER","PLATINUM","CRUDE","USJUNK","USGOVT10","USCORP")] %>% na.omit()

b <- prices[,c("Dates","BTC","LTC","XRP","ETH")]

ret2 <- as.xts(b[,-c(1)],order.by = b$Dates) %>% Return.calculate()
  
ret <-  as.xts(a[,-c(1)],order.by = a$Dates) %>% Return.calculate()

returns <- cbind.xts(ret2,ret)

returns_df <- as.data.frame(returns)

returns_df <- cbind(Dates = index(returns),returns_df)

mreturns <- melt(returns_df, id.vars = ("Dates"))

 

z <- ggplot(data = mreturns, aes(x = value, y = variable, group = variable))+ geom_jitter(alpha = 0.1, color = "grey") + geom_boxplot(alpha = 0.3, lwd = 0.5, color = "black", outlier.shape = NA) + theme_classic() + theme(strip.background = element_blank()) + xlab("Daily Returns") + ylab("") + scale_x_continuous(breaks = round(seq(min(mreturns$value, na.rm = TRUE), max(mreturns$value, na.rm = TRUE), by = 0.25),2)) + ylab("Assets")

ggsave("AssetBox.pdf",z, height = 5, width = 6)

```


